---
title: "p8105_hw1_rw3033"
output: github_document
---


# Problem 1

Load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

Describe the dataset
```{r}
library(tidyverse)
names(penguins)
nrow(penguins)
ncol(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
Description:
There are 3 kinds of penguin species.
The dataset contains 344 rows and 8 columns.
The 8 variables (column names) include: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year.
The mean flipper length is 200.9152 mm.


Make a scatterplot
```{r}
library(ggplot2)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(title = "Flipper Length vs. Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)",
       color = "Species")
```
Export the scatterplot
```{r}
ggsave("scatterplot_penguins.png")
```


# Problem 2

Create a data frame
```{r}
library(tidyverse)

random_sample = rnorm(10)
logical_vector = random_sample > 0
character_vector = letters[1:10]
factor_vector = factor(rep(c("low", "medium", "high"), length.out = 10)) 

df = tibble(
  random_sample = random_sample,
  logical_vector = logical_vector,
  character_vector = character_vector,
  factor_vector = factor_vector
)

view(df)

```

Calculate the means of each variable
```{r}
mean(pull(df, random_sample))
mean(pull(df, logical_vector))
mean(pull(df, character_vector))
mean(pull(df, factor_vector))

```

Description:
random_sample works, since it is numeric;
logical_vector works, since logical TRUE is treated as 1 and FALSE as 0;
character_vector gives an error, since characters cannot be averaged;
factor_vector gives an error, since factors are categorical, not numeric.



Write a code chunk that applies the as.numeric function to the logical, character, and factor variables 
```{r}
as.numeric(pull(df,logical_vector))  
as.numeric(pull(df,character_vector)) 
as.numeric(pull(df,factor_vector))
```

Description:
as.numeric(df$random_sample)  works, since it is already numeric;
as.numeric(df$logical_vector) works, as TRUE becomes 1, FALSE becomes 0;
as.numeric(df$character_vector) gives an error, since characters cannot be converted;
as.numeric(df$factor_vector) works, it converts factor levels to their vector levels. Since these numbers denotes the vector levels, they do not make sense in calculating the mean.